\documentclass{journal}

\usepackage[super, sort]{natbib}
  \bibpunct{(}{)}{;}{a}{,}{,} % required for natbib  
\bibliographystyle{authordate2}


\title{Lab Notebook}
\author{Brooke Bothwell}
\date{April 28, 2015}
\begin{document}
	\maketitle 
	\section*{Tuesday, April 28, 2015}
Today I am starting my lab notebook. As well as attempting to work with the Latex software and Github. However, it is proving difficult. I am not exactly sure how to push my data to the github cite, or pull from the github cite. My meeting is tomorrow at 11:00 and the only thing I am going to have to show for it is this entry in this lab notebook. I have been looking at forums only and trying to figure out how to push/pull with github from the command line however I am still having difficulties.
		\paragraph{Latex and Github}
Writing in these is not that difficult, however I am having a problem pushing and pulling. (Thinking about creating my own private journal using this for practice, could be easy to organize and would say on money and the environment).	

\section*{Wednesday, April 29, 2015}
Meeting with Dr. Borrett today going over Github and Latex software and how to use it with the DIS. Very productive meeting. Actually learned a lot about how to work with the software and how to use it not just within the DIS program. This is awesome.
\paragraph{Working with equations and testing citations}

We are testing the citation out.  Here is a indirect effects paper \citep{patten1995}.

Opps, I forgot to insert an equation
\begin{equation}
E = mc^2
\end{equation}


Lets write an equation.
\begin{equation}
y = mx + b  \label{eq:line}
\end{equation}
\paragraph{Rstudio} The next step is to introduce the actual Network software into the Rstudio system on my computer and I will have the whole lab on my computer! Yay!

Now I can reference my equation directly by saying see equation~\ref{eq:line}
\bibliography{temp}

\end{document}